Paper Analysis

### 2024-07-22 Paper_WriteUp/Paper_Plots.qmd
adding in some more stuff

>>>>

## 2000-2200 Previous Game

data_path <- here("results/lichess2000-2200_mar")

fit_20_22_bullet_prev <- 
  readRDS(file =paste0(data_path,"/all_rated_bullet_model_prev.RDS"))

fit_20_22_bullet_prev$summary(variables = c("mu_beta",
                                            "gamma1", "gamma2",
                                            "sigma_1", "tau[1]", "tau[2]",
                                            "sigma_g1", "sigma_g2"))
```

## 2300-2500 Previous Game

data_path <- here("results/lichess2300-2500_mar")

fit_23_25_bullet_prev <- 
  readRDS(file =paste0(data_path,"/all_rated_bullet_model_prev.RDS"))

fit_23_25_bullet_prev$summary(variables = c("mu_beta",
                                            "gamma1", "gamma2",
                                            "sigma_1", "tau[1]", "tau[2]",
                                            "sigma_g1", "sigma_g2"))
```
